Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2016-05-02 manuscript.tex
Add correct link to SEG software archive
Fixes #8
Cite figure from figshare
Fixes #5
Separate the table to another file
Fixes #11

\address{Peer-reviewed code related to this article can be found at
http://software.seg.org/2016/000X.
\\
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\\
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
email: valcris@on.br
\\
\footnotemark[3]Department of Mathematics and Geosciences,
University of Trieste, Trieste, Italy
}

@@

\begin{figure}
    \centering
    \includegraphics{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{table*}
\centering
\begin{tabular}{lccc}
    \hline
    ~             & Grid location & Grid height & Tesseroid size \\
    \hline
    Experiment 1 (pole)            & 89N--90N/0E--1E  & 2 km   & $1^\circ \times 1^\circ$ \\
    Experiment 2 (equator)         & 0N--1N/0E--1E    & 2 km   & $1^\circ \times 1^\circ$ \\
    Experiment 3 (260 km)          & 89N--90N/0E--1E  & 260 km & $1^\circ \times 1^\circ$ \\
    Experiment 4 ($30^\circ$ size) & 60N--90N/0E--30E & 2 km   & $30^\circ \times 30^\circ$ \\
    \hline
\end{tabular}
\caption{
    Parameters of the numerical experiments to quantify the accuracy of
    the numerical integration.
    All grids had $10\times10$ regularly spaced computation points at a
    constant height.
    Tesseroids used to discretize the spherical shell had 1 km thickness and
    the horizontal dimensions shown in the table.
}
\label{tbl:experiment}
\end{table*}

>>>>

\address{Peer-reviewed code related to this article can be found at
http://software.seg.org/2016/0004.
\\
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\\
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
email: valcris@on.br
\\
\footnotemark[3]Department of Mathematics and Geosciences,
University of Trieste, Trieste, Italy
}

@@

\begin{figure}
    \centering
    \includegraphics{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\input{table1.tex}
